On the combination of Set Functions and Failures

### 2014-11-19 docs/src/usage.tex
Added explanation of (+/-)(trace/profile) to manual, changelog extended

>>>>

\item[\fbox{\code{+/-trace}}]\pindex{trace}
Turn on/off the trace mode. If the trace mode is on,
it is possible to trace the sources of failing computations.

\item[\fbox{\code{+/-profile}}]\pindex{profile}
Turn on/off the profile mode. If the profile mode is on,
expressions as well as programs are compiled with GHC's profiling
capabilities enabled. For expressions, evaluation will automatically
generate a file \code{Main.prof} containing the profiling information
of the evaluation.
For compiled programs, the profiling has to be manually activated
using runtime options when executed:
\begin{curry}
kics2 :set +profile :load MyProgram.curry :save :quit
./MyProgram +RTS -p -RTS [additional arguments]
\end{curry}
